\documentclass[a4paper,10pt]{article}

\usepackage[left=0.6in,right=0.6in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

% --------- Section Formatting ----------
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{5pt}{2pt}

% --------- List Spacing ----------
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.2em}

% --------- Hyperlink Styling ----------
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue}

\begin{document}

% --------- Header ----------
\begin{center}
    {\LARGE \textbf{Sambhav Jain}} \\[2pt]
    Mysore, India \textbar{} Open to relocation \\[2pt]
    \href{mailto:13sambhavjain@gmail.com}{13sambhavjain@gmail.com} \quad
    +91-9009306660 \quad
    \href{https://github.com/13sambhavjain}{github.com/13sambhavjain} \quad
    \href{https://linkedin.com/in/13sambhavjain}{linkedin.com/in/13sambhavjain}
\end{center}

% --------- Summary ----------
\section*{Summary}

Software Engineer with experience in Python-based system development, modular architecture, and reusable tooling design. Skilled in building configurable workflows, developer-focused APIs, and scalable engineering utilities with strong interest in designing reliable and extensible software systems.

% --------- Experience ----------
\section*{Experience}

\noindent
\textbf{Engineer} \hfill \textit{Mar 2026 -- Present} \\
\textit{L\&T Technology Services (Client: Bose), Mysore}

\textit{Protocol Validation and Command Engineering}

\begin{itemize}

\item Developing Python-based validation workflows involving reverse engineering of variable-to-address mappings within proprietary software environments.

\item Designing command-generation pipelines supporting automated validation of protocol-level operations.

\item Reusing and extending modular framework components to support new validation workflows.

\end{itemize}

\textit{Framework Refinement}

\begin{itemize}

\item Enhancing reliability and extensibility of configuration-driven protocol workflows used across engineering teams.

\item Improving maintainability of reusable communication modules and execution pipelines.

\end{itemize}

\vspace{3pt}

\noindent
\textbf{Associate Engineer} \hfill \textit{Dec 2024 -- Feb 2026} \\
\textit{L\&T Technology Services (Client: Bose), Mysore}

\textit{Modular Protocol Framework Development}

\begin{itemize}

\item Designed and developed a modular Python-based protocol abstraction framework integrating libraries including \textbf{python-can, pyserial, udsoncan, and isotp}.

\item Built reusable API layers supporting dynamic communication workflows across CAN, UDS, and Serial interfaces.

\item Designed configuration-driven architecture enabling project-specific workflows through structured configuration modules and runtime injection of client extensions.

\item Implemented extensible plugin-style client system allowing dynamic addition of custom protocol functionality.

\item Developed automated workspace scaffolding utilities generating project templates, configuration modules, extension structures, and usage scripts.

\item Designed developer-friendly APIs enabling concise scripting where complex operations could be expressed through minimal commands.

\item Implemented type-safe configuration templates using Python type annotations and TYPE\_CHECKING constructs to improve IDE support and developer productivity.

\item Enabled adoption across multiple engineering teams, improving workflow consistency and reducing repetitive setup effort.

\item Implemented automated stress-testing workflows supporting large-scale batch execution of communication operations.

\item Reverse engineered proprietary communication protocols and implemented reusable Python interfaces for command decoding and execution.

\end{itemize}

\textit{Static Code Analysis Development}

\begin{itemize}

\item Developed Python-based static analysis utility using AST parsing to detect function-level changes across C source revisions.

\end{itemize}

% --------- Projects ----------
\section*{Projects}

\noindent
\textbf{cubekit — Python Package (PyPI)}

\begin{itemize}

\item Developed and published modular Python package implementing human-style Rubik's Cube solving workflows using extensible cube modeling and structured solver pipelines.

\item Designed reusable abstractions supporting configurable solver workflows and validated reliability across millions of randomized cube states.

\item PyPI: \href{https://pypi.org/project/cubekit/}{pypi.org/project/cubekit} \quad GitHub: \href{https://github.com/13sambhavjain/cubekit}{github.com/13sambhavjain/cubekit}

\end{itemize}

\vspace{2pt}

\noindent
\textbf{Modular Card Game Simulator (In Progress)}

\begin{itemize}

\item Designing extensible multiplayer card engine supporting customizable rule systems and modular gameplay logic.

\end{itemize}

\vspace{2pt}

\noindent
\textbf{Minesweeper AI}

\begin{itemize}

\item Implemented knowledge-based AI agent capable of identifying safe moves using logical inference.

\end{itemize}

% --------- Technical Skills ----------
\section*{Technical Skills}

\textbf{Languages:} Python (Primary), C++, SQL \\
\textbf{Core:} Data Structures \& Algorithms, Object-Oriented Programming, API Design, Modular Architecture, Dependency Injection \\
\textbf{Tools:} Git, Linux, Django \\
\textbf{Systems:} Communication Protocols, Protocol Abstraction, Reverse Engineering

% --------- Education ----------
\section*{Education}

\noindent
\textbf{B.E. Computer Engineering} \hfill \textit{Graduated 2024} \\
\textit{IET DAVV, Indore} \hfill CGPA: \textbf{8.07}

% --------- Achievements ----------
\section*{Achievements}

\begin{itemize}

\item Published Python package on PyPI (\textbf{cubekit}).

\item GRE Score: \textbf{329} (170 Quant, 159 Verbal).

\item IELTS: Overall \textbf{7.5}

\end{itemize}

\end{document}
