\documentclass[a4paper,10pt]{article}

\usepackage[left=0.6in,right=0.6in,top=0.65in,bottom=0.65in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

% --------- Section Formatting ----------
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{10pt}{4pt}

% --------- List Spacing ----------
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.2em}

% --------- Hyperlink Styling ----------
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue}

\begin{document}

% --------- Header ----------
\begin{center}
    {\LARGE \textbf{Sambhav Jain}} \\[4pt]
    Mysore, India \textbar{} Open to relocation \\[2pt]
    \href{mailto:13sambhavjain@gmail.com}{13sambhavjain@gmail.com} \quad
    +91-9009306660 \quad
    \href{https://github.com/13sambhavjain}{github.com/13sambhavjain} \quad
    \href{https://linkedin.com/in/13sambhavjain}{linkedin.com/in/13sambhavjain}
\end{center}

\vspace{2pt}

% --------- Summary ----------
\section*{Summary}
Computer Engineering graduate with strong foundations in Data Structures, Algorithms, and Python-based system development. Currently building modular frameworks and developer tooling for automotive systems at L\&T Technology Services. Experienced in designing scalable systems, abstraction layers, and reusable APIs. Interested in backend and systems-oriented software engineering roles.

% --------- Skills ----------
\section*{Technical Skills}
\textbf{Languages:} Python, C++, SQL, JavaScript \\
\textbf{Core Concepts:} Data Structures \& Algorithms, Object-Oriented Programming, Operating Systems, DBMS \\
\textbf{Technologies:} Python (advanced), Django (learning), Git, Linux \\
\textbf{Systems Exposure:} CAN, UDS, Serial Communication (BDP), ECU basics

% --------- Experience ----------
\section*{Experience}

\noindent
\textbf{Associate Engineer Trainee} \hfill \textit{2024 -- Present} \\
\textit{L\&T Technology Services (Client: Bose), Mysore}

\begin{itemize}
    \item Designed and developed \textbf{Canopy}, a modular Python-based framework replacing legacy ATP/.NET workflows, enabling execution on standard developer machines.
    
    \item Built reusable abstraction layers for \textbf{3+ communication protocols (CAN, UDS, Serial)}, simplifying interaction with ECU systems.
    
    \item Reverse engineered proprietary protocols (BDP, A2B) and exposed them through clean Python APIs.
    
    \item Developed data acquisition pipelines using PicoScope SDK for real-time signal capture and analysis.
    
    \item Designed extensible APIs for command execution, response parsing, and logging.
    
    \item Enabled adoption across \textbf{5+ projects and $\sim$20+ engineers}, reducing repetitive setup effort and improving scalability.
    
    \item Worked across multiple client projects involving system automation and tooling development.
\end{itemize}

\noindent
\textbf{Software Intern} \hfill \textit{2023} \\
\textit{Walkover, Indore}

\begin{itemize}
    \item Built JavaScript-based plugins integrating multiple REST APIs (GET/POST) for data-driven workflows.
    
    \item Implemented API-driven data retrieval and transformation pipelines.
\end{itemize}

% --------- Projects ----------
\section*{Projects}

\noindent\textbf{Rubik’s Cube Solver}
\begin{itemize}
    \item Built a Python-based solver implementing human solving algorithms for step-by-step solutions.
    \item \href{https://github.com/13sambhavjain/Cube-Solver}{github.com/13sambhavjain/Cube-Solver}
\end{itemize}

\noindent\textbf{Modular Card Game Simulator}
\begin{itemize}
    \item Designing a modular multiplayer card game engine in Python supporting customizable game logic.
\end{itemize}

\noindent\textbf{Minesweeper AI}
\begin{itemize}
    \item Developed a knowledge-based AI agent using logical inference.
\end{itemize}

\noindent\textbf{Static Code Analysis Tool}
\begin{itemize}
    \item Built a Python-based tool using AST parsing to compare C code versions and identify impacted components.
\end{itemize}

% --------- Education ----------
\section*{Education}

\noindent
\textbf{B.E. Computer Engineering} \hfill \textit{Graduated 2024} \\
\textit{IET DAVV, Indore} \hfill CGPA: \textbf{8.07}

% --------- Achievements ----------
\section*{Achievements \& Certifications}

\begin{itemize}
    \item Solved \textbf{500+ Data Structures and Algorithms problems} on LeetCode
    \item GRE Score: \textbf{329} (170 Quant, 159 Verbal)
    \item IELTS: \textbf{8.0} (L), \textbf{8.0} (R), \textbf{8.0} (S), \textbf{6.5} (W)
    \item Meta Backend Developer Certification (4/9 courses completed)
    \item Mastering C++ (Abdul Bari), Data Structures \& Algorithms (Udemy)
\end{itemize}

\end{document}
